Supervision

### 2024-10-16 supervision.qmd
update

Specific projects I am currently seeking students for are [here](https://docs.google.com/document/d/1v9akVLjoYlR01V7SvGjYxUsDP2zCCbdvSXYB1NqoqcQ/edit?usp=sharing). Some advice about applying is [here](https://github.com/tomstafford/onboarding/).

>>>>

I am not currently accepting applications for PhD places. My old advice page about applying is [here](https://github.com/tomstafford/onboarding/).
